Analysis and elimination of bottlenecks\\ in parallel algorithm for solving\\ global optimization problems

### 2022-06-10 2022/RSD/paper.tex
after review

The first iteration of the method is performed in a special way. The trials are performed at the boundary points $x^0 = 0$ and $x^1 = 1$ as well as at $(p-2)$ arbitrary different internal points $x^2, x^3, ..., x^{p-1}$ in the interval $[0,1]$.

@@

The theoretical basis of the presented algorithm (denoted hereafter as \textit{global search algorithm} or GSA) see in more details in \cite{Strongin2000}. Note briefly that the characteristics of the intervals (\ref{R}) used in the algorithm can be considered as a quantitative measure how particular interval is promising from the viewpoint of finding the global minimum inside it. The inequalities (\ref{OrderedR}) arrange the intervals according to their characteristics, and the trials are performed in parallel in $p$ most promising intervals.

>>>>

The first iteration of the method is performed in a special way. The trials are performed at the boundary points $x^0 = 0$ and $x^1 = 1$ as well as at $(p-2)$ arbitrary different internal points $x^2, x^3, ..., x^{p-1}$ in the interval $[0,1]$.
After executing the first iteration of the method, i.e. at $n=1$, the number of trials will be $k=p$.
%After the first iteration, i.e. at $n=1$, the number of trials will be $k=p$.

@@

The theoretical basis of the presented algorithm (denoted hereafter as \textit{global search algorithm} or GSA) see in more details in \cite{Strongin2000,Strongin2018}. Note briefly that the characteristics of the intervals (\ref{R}) used in the algorithm can be considered as a quantitative measure how particular interval is promising from the viewpoint of finding the global minimum inside it. The inequalities (\ref{OrderedR}) arrange the intervals according to their characteristics, and the trials are performed in parallel in $p$ most promising intervals.
